---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(giantbomb)
```

[![Travis-CI Build Status](https://travis-ci.org/detroyejr/giantbomb.svg?branch=master)](https://travis-ci.org/detroyejr/giantbomb)

The giantbomb package provides access to the [GiantBomb API] (https://www.giantbomb.com/api/) which gives information on video games, reviews, companies, and other related content.

# Install

Install the package using devtools.

```{r, eval = FALSE}
devtools::install_github("detroyejr/giantbomb")
```

At the time this package was created, these endpoints are covered:

* `gb_search`
* `gb_games`
* `gb_companies`
* `gb_characters`
* `gb_reviews`
* `gb_platforms`
* `gb_franchises`

## API Key

Before you can begin to use the giantbomb package, you will need to [sign up](https://www.giantbomb.com/signup/) to receive an api key. Once you login, your key will appead on the [main api page](https://www.giantbomb.com/api/).

Once you have your key, you can either pass it as a string to the `api_key` function parameters or set the `GB_KEY` environoment variable.

```{r, eval = FALSE}
Sys.setenv("GB_KEY" = 'YOUR_API_KEY`)
```

The function `gb_key()` will look in the system environment for a variable with that name.

## Examples

### Basic Usage

```{r}
# Get list of games.
gb_games(n = 10, field_list = c("date_added", "name"))

# Get list of companies.
gb_companies(n = 10, field_list = c("date_added", "name"))
```

### Filters and Sorting

```{r}
# Filter by name and sort by date_added.
gb_games(
  n = 10,
  filter = "name:bioshock",
  sort = "date_added:desc",
  field_list = c("name", "date_added")
  )

# Filter companies by name and sort by date_added.
gb_companies(
  n = 10,
  filter = "name:2k",
  sort = "date_added:asc",
  field_list = c("name", "date_added")
  )
```

For more examples, look in the function documentation.

## Contributing

If you find any bugs, you can file an issue or create a pull request.
